%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{cv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Roman Niukhalov}
\address{Bangkok, Thailand}
\contacts{+66 (97) 002-9407 \linebreak r.nyukhalov@gmail.com}

\begin{document}

	% Print the header
	\makeheader

	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{Agoda}{Summer 2017 -- Present}
			\begin{itemize}
				\item Reduced the end-to-end time of updating hotels' prices from several minutes to tens of seconds by re-designing and optimizing internal services.
				\item Reduced the load on the internal monitoring system by more than 1000\% by aggregating measurements on clients before sending them to the system.
        \item Reduced the number of missed phone calls to a person on call by creating a slack bot reminding one when (s)he is on call.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{2GIS}{Winter 2015 -- Summer 2017}
			\begin{itemize}
				\item Created with a team an automated pipeline for importing geodata from OpenSteetMap.
				\item Created a geosearch API for querying geodata features by a feature class and a bounding box.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Center of Financial Technologies}{Spring 2013 -- Winter 2015}
			\begin{itemize}
        \item Developed a Java library for performing contactless payments using Android Host-base Card Emulation.
        \item Developed with a team firmware for Point-of-Sale (POS) terminals.
        \item Reduced time of testing firmware for JavaCard applets by creating an automated testing framework.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}

	\begin{cvsection}{Education}
    \begin{cvsubsection}{Udacity}{}{Summer 2018 -- Winter 2019}
			\begin{itemize}
				\item Self-Driving Car Engineer Nanodegree Program.
				\item Coursework: Computer Vision; Sensor Fusion; Localization; Motion Control; Path Planner.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Novosibirsk, Russia}{Novosibirsk State Technical University}{Fall 2007 -- Summer 2011}
			\begin{itemize}
				\item B.S.E. in Applied Mathematics and Computer Science, June 2011.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Linear Algebra; Calculus.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Course Projects}{}{}
			\begin{itemize}
				\item \textbf{Advanced Lane Finding} (2018). A software pipeline to identify the lane boundaries in a video. The pipeline consists of several computer vision techniques such as color and gradient thresholding, and perspective transformation.
				\item \textbf{Traffic Sign Recognition} (2018). A convolutional neural network for classifying traffic sign images using the German Traffic Sign Dataset.
				\item \textbf{Behavioral Cloning} (2018). A convolutional neural network for predicting the steering angle of the simulated vehicle by images from its camera.
				\item \textbf{Extended Kalman Filter} (2018). Kalman Filter implementation to estimate the state of a moving object of interest with noisy lidar and radar measurements.
				\item \textbf{Kidnapped Vehicle} (2018). Particle Filter implementation to localize an object by noisy GPS coordinates.
				\item \textbf{Highway Driving} (2019). A behaviour planning program to safely navigate the simulated car around a virtual highway with other traffic.
				\item \textbf{PID Controller} (2019). PID Controller implementation to control the simulated car's steering angle.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item C++; C; Java; Scala; Python
				\item Intellij Idea; Git; PostgreSQL; Cassandra; Couchbase; Kafka
				\item Docker; Docker Compose; Kubernetes
				\item Jenkins, Gitlab CI, Teamcity, Bamboo
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

\end{document}
